Light inextensible strings (thread) under tension in the Schwarzschild geometry

### 2021-01-26 physics_educator_rebuttal.txt

> 6. Local observer (page 4 line 7) I believe the author means static
> observer in Schwarzschild coordinates.

I realise that I have been misusing the word "local" to mean "static"
and have now corrected the manuscript.

>  
> 7. Radius of curvature (page 4 line 7) Since the equatorial plane is
> now curved, what radius of curvature is the author talking about?
> Clarification is needed.

On re-reading, the original manuscript was a little cryptic.  I have
added a detailed derivation of this result that should clarify the
issue.  In essence, a light beam and a tangential string will diverge
quadratically and this leads to the radius of curvature quoted.

@@

>  
> 8. A radius of \sqrt{27M} (page 4 line 9) What radius is this?

Derivation added as a result of point 7 above should clarify this
issue.

### 2021-01-26 string_physics_educator_revision2.tex
fixes #30 fixes #31

There does not appear to be a simple analytical solution to
equation~\ref{rdashdash}; but it is a straightforward second order
ODE, amenable to numerical solution and no harder than the equivalent
for null geodesics, a standard homework problem.  Here we consider
only strings exterior to the event horizon, $r>2M$, which have a
well-defined point of closest approach to the singularity.  Because
the system is invariant under~$\phi\longrightarrow-\phi$, the string
must be symmetrical about this point.  If $\phi'$ is small, then a
string follows $r''=r-2M$, while tangential null geodesics follow
$r''=r-3M$.  Thus a taut string would {\em look} curved to a local
observer, having a (visual) radius of curvature of
$r_0^2/M\sqrt{1-2M/r_0}$ (the extra term comes from the fact that
appearance is driven by local $ds$, not Schwarzschild $r$).  At the
photon sphere $r_0=3M$, such a string would appear to have a radius
of~$\sqrt{27}M$.  For a solar mass black hole this would be about
$15\unit{km}$, a readily understandable result.

>>>>

There does not appear to be a simple analytical solution to
equation~\ref{rdashdash}; but it is a straightforward second order
ODE, amenable to numerical solution and no harder than the equivalent
for null geodesics, a standard homework problem.  Here we consider
only strings exterior to the event horizon, $r>2M$, which have a
well-defined point of closest approach to the singularity.  Because
the system is invariant under~$\phi\longrightarrow-\phi$, the string
must be symmetrical about this point.  If $r'$ is small, then a string
follows $r''=r-2M$, while tangential null geodesics follow $r''=r-3M$.
Working to first order, and writing~$d$ for the difference in
Schwarzschild $r$ between string and null geodesic, we see that
$d''=M$.  Transforming coordinates to $(x,y) = (r\phi,r-r_0)$ and with
boundary conditions corresponding to a string and null geodesic
tangential at the $(x,y)$ origin, we see that
$d=\frac{M}{2}(x/r_0)^2$.  However, a static local observer tied to
the string would measure
$d_\mathrm{local}=d/\sqrt{1-2M/r_0}$---applying
equation~\ref{schwarzschild}---and obtain
$d_\mathrm{local}=\frac{M}{2}(x/r_0)^2\left(1-2M/r_0\right)^{-1/2}$
which would correspond to a radius of curvature
of~$r_0\cdot\frac{r_0}{M}\cdot\left(1-2M/r_0\right)^{-1/2}$.  Thus a
taut string would {\em look} curved to a static observer in
Schwarzschild coordinates, in the sense that a tangential light beam
and taut string would diverge quadratically.  At the photon sphere
$r_0=3M$, such a string would appear to have a radius of~$\sqrt{27}M$.
For a solar mass black hole this would be about $15\unit{km}$, a
readily understandable result.
